### 2016-09-07 results.tex
cheers

%%%%%%%%%%
\input{ds-ss-proof}
%%%%%%%%%%

>>>>

%%%%%%%%%%
\begin{theorem}
Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$ 
\[
\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.) 
\end{theorem}
\begin{proof}[Proof (sketch). ]
Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\Pi_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.  When~$f=F_K$ then the simulation is perfect.  When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\Pi}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.  But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.  Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
\end{proof}
%%%%%%%%%%
